---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# japanmesh

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/japanmesh)](https://CRAN.R-project.org/package=japanmesh)
<!-- badges: end -->

japanmesh is an R package for using the reference regional mesh (1st to 3rd), the split regional mesh as defined by the JIS (Japan Industrial Standard) X 0410 '[regional mesh code](https://www.jisc.go.jp/app/jis/general/GnrJISNumberNameSearchList?show&jisStdNo=X0410)' and 1/10 subdivision of the 3rd mesh.
Regional mesh codes are square-like regional divisions set up for all regions of Japan based on longitude and latitude. For more information on regional meshes, please check [the Statistics Bureau of Japan page](https://www.stat.go.jp/data/mesh/pdf/gaiyo1.pdf).

A summary of the regional mesh codes is shown below.

```{r,echo=FALSE}
df <- tibble::tibble(`Name` = c("the 1st mesh", "the 2nd mesh", "the 3rd mesh", "the 1/2 mesh", "the 1/4 mesh", "the 1/8 mesh", "1/10 subdivision of the 3rd mesh"),
                     `Length` = c("Abount 80km", "Abount 10km", "Abount 1km", "Abount 500m", "Abount 250m", "Abount 125m", "Abount 100m"),
                     `Number of digits` = c(4, 6, 8, 9, 10, 11, 10))
knitr::kable(df)
```

japanmesh has been developed to enable faster processing than the R package [jpmesh](https://github.com/uribo/jpmesh).
The main differences between japanmesh and jpmesh are as follows

1. Explicitly given a mesh size (such as `mesh_80km`). 
2. Non-land (ocean) meshes are supported.
3. It can extract nth-order neighboring meshes and perform complex operations such as extracting meshes and calculating the distance of (line) paths between meshes.

## Installation

You can install japanmesh from CRAN.

``` r
install.packages("japanmesh")
```

You can also install the development version from GitHub.

``` r
# install.packages("devtools")
devtools::install_github("UchidaMizuki/japanmesh")
```
## Usage

```{r,message=FALSE,warning=FALSE}
library(japanmesh)

library(tibble)
library(dplyr)
library(ggplot2)
```

### Generation of regional mesh codes from character strings or numbers

Use functions such as `mesh_80km()`, `mesh_auto()`, etc. to generate regional mesh codes from strings or numbers.

- The `mesh_auto()` function automatically determines the mesh size.
- The default (`strict = TRUE`) requires the mesh codes to have a given number of digits.

```{r}
library(japanmesh)

x <- c("53394526313", "5339358633", "533945764", "53394611", "523503", "5339", NA)

mesh_80km(x)
mesh_125m(x)
mesh_auto(x)

mesh_80km(x, strict = F)
mesh_125m(x, strict = F)
mesh_auto(x, strict = F)
```

### Converting the mesh size of regional mesh codes

Use functions such as `mesh_80km()` to coarsen the mesh size of regional mesh codes.
The `mesh_subdivide()` function can be used to subdivide regional mesh codes.

- `mesh_subdivide()` outputs a list of mesh codes whose elements are contained in the original meshes.
- The conversion between 500m mesh and 100m mesh is supported.

```{r}
mesh500m <- mesh_500m("533945764")

mesh_1km(mesh500m)

mesh100m <- mesh_subdivide(mesh500m,
                           size = "100m")
mesh100m

tibble(mesh100m = mesh100m[[1]]) %>% 
  mutate(polygon = mesh_to_polygon(mesh100m)) %>% 
  sf::st_as_sf() %>%
  
  ggplot() +
  geom_sf() +
  geom_sf_text(aes(label = mesh100m))
```

### Conversion from longitude/latitude to regional mesh codes

The `XY_to_mesh()` function converts longitude and latitude to regional mesh codes.

```{r}
tibble(X = c(139.7008, 135.4375), # longitude
       Y = c(35.68906, 34.70833)) %>% # latitude
  mutate(mesh100m = XY_to_mesh(X, Y, size = "100m"),
         mesh125m = XY_to_mesh(X, Y, size = "125m")) %>% 
  knitr::kable()
```

### Conversion from regional mesh codes to longitude/latitude

The `mesh_to_XY()` function converts regional mesh codes to longitude and latitude.

```{r}
tibble(mesh = c("5339452660", "5235034590")) %>% 
  mutate(mesh %>% 
           mesh_100m() %>% 
           mesh_to_XY()) %>% 
  knitr::kable()
```

### Calculation of adjacent mesh codes

The `mesh_neighbor()` function calculates the neighboring meshes.

- nth order neighboring meshes can be calculated by specifying `n`.
- Can be calculated in a Neumann neighborhood with `moore = FALSE`.

```{r}
neighbor <- mesh_10km("644142") %>% 
  mesh_neighbor(n = c(0:2),
                simplify = FALSE)

neighbor[[1]] %>% 
  mutate(geometry = mesh_to_polygon(mesh_neighbor)) %>% 
  sf::st_as_sf() %>% 
  
  ggplot(aes(fill = as.factor(n))) +
  geom_sf() +
  geom_sf_text(aes(label = mesh_neighbor))
```

```{r}
neighbor_neumann <- mesh_10km("644142") %>% 
  mesh_neighbor(n = c(0:2),
                simplify = F,
                moore = F)

neighbor_neumann[[1]] %>% 
  mutate(geometry = mesh_to_polygon(mesh_neighbor)) %>% 
  sf::st_as_sf() %>% 
  
  ggplot(aes(fill = as.factor(n))) +
  geom_sf() +
  geom_sf_text(aes(label = mesh_neighbor))
```

### Draw line segments between meshes

The `mesh_line()` function extracts meshes that lie on the line segments between meshes.

```{r}
mesh_from <- mesh_80km(c("6441", "5339"))
mesh_to <- mesh_80km(c("5237", "5235"))

line <- mesh_line(mesh_from, mesh_to)

print(line)
plot(line[[1]])
```

It can handle the case of passing through multiple meshes by giving a `list` of meshes.

- Close the line segment with `close = TRUE`.
- `skip_na = TRUE` to skip `NA`.

```{r}
mesh_1 <- mesh_80km(c("6441", "5339", NA, "5250"))
mesh_2 <- mesh_80km(c("6439", "5211", "4013", "6635"))

line <- mesh_line(list(mesh_1, mesh_2), 
                  close = TRUE,
                  skip_na = TRUE)

print(line)
plot(line[[1]])
```

### Calculation of distance between meshes

The `mesh_distance()` function calculates the distance between meshes (great circle distance).

- As with `mesh_line()`, the path distance can be calculated by `list` of meshes.

```{r}
mesh_from <- mesh_80km(c("6441", "5339"))
mesh_to <- mesh_80km(c("5237", "5235"))

distance <- mesh_distance(mesh_from, mesh_to)

print(distance)
```

### Others
- The `mesh_move()` function can be used to calculate regional meshes in the east-west and north-south directions.
- The `mesh_to_polygon()` and `mesh_to_point()` functions can output `sfc` geometry.
- For meshes outside the range of the 80 km mesh, where the digits are negative or exceed three digits, the relevant code is displayed as `<-1>` or `<123>` to clearly distinguish them from existing meshes.

## Comparison of processing speed with jpmesh package

The conversion speed between meshes and latitude/longitude in this package is several hundred times faster than in the `jpmesh` package.

```{r,echo=FALSE,message=FALSE}
set.seed(1234)
X <- runif(1e1, 139, 140)
Y <- runif(1e1, 39, 40)

microbenchmark::microbenchmark(`japanmesh::XY_to_mesh()` = XY_to_mesh(X, Y,
                                                                    size = "1km"),
                               `jpmesh::coords_to_mesh()` = jpmesh::coords_to_mesh(X, Y,
                                                                                 mesh_size = 1)) %>% 
  autoplot()
```

```{r,echo=FALSE,message=FALSE}
set.seed(1234)
X <- runif(1e1, 139, 140)
Y <- runif(1e1, 39, 40)
mesh_japanmesh <- XY_to_mesh(X, Y,
                             size = "1km")
mesh_jpmesh <- jpmesh::coords_to_mesh(X, Y, 
                                      mesh_size = 1)

microbenchmark::microbenchmark(`japanmesh::mesh_to_XY()` = mesh_to_XY(mesh_japanmesh),
                               `jpmesh::mesh_to_coords()` = jpmesh::mesh_to_coords(mesh_jpmesh)) %>% 
  autoplot()
```
